A Gentle Introduction and Application of Feature-Based Clustering with Psychological Time Series

### 2023-02-24 manuscript.tex
:memo: discussion notes

@@

NOTES:
The clustering of model parameters is, thus, technically a restrictive sub-form of feature-based clustering --- where lagged regression coefficients, for example, can be considered to be one type of feature capturing a time series. However, beyond model parameters, time series might also be described with any other statistical feature \citep{tiano2021}.

---

>>>>

\begin{center}
\rule{0.4\textwidth}{.4pt}
\end{center}

\textbf{NOTES:}

The clustering of model parameters is, thus, technically a restrictive sub-form of feature-based clustering --- where lagged regression coefficients, for example, can be considered to be one type of feature capturing a time series. However, beyond model parameters, time series might also be described with any other statistical feature \citep{tiano2021}.

@@

\begin{center}
\rule{0.4\textwidth}{.4pt}
\end{center}
